---
title: "Data Access"
author: ""
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
---

## Introduction
This notebook downloads and pre-processes the raw data sets used for this project.

## Dependencies
This notebook requires a number of `R` packages:

```{r load-packages}
# tidyverse packages
library(dplyr)        # data wrangling
library(readr)        # read/write csv files

# other packages
library(here)         # file path management
```

Additionally, `Hmisc` is used below. It is not loaded here because it overwrites a large number of functions and methods and is used for one function only. It will be called with `Hmsic::mdb.get()`. You will also need `mdb-tools` installed on Unix/Linux machines for this function to work. On macOS - use `brew install mdbtools` to get that installed.

## Create Temporary Directory
All of the data sets are going to be passed through a temporary directory to avoid creating intermediary files and objects. We'll create the temporary directory first, and continue to refer to the `tmp` path in subsequent functions:

```{r create-temp}
tmp <- tempdir()
```

## Load Vacancy Data
First, we'll load the vacancy data. They're stored in a zipped `.csv` file that can be found in `data/raw/nearby vacant parcels summary.zip`. The `.csv` is too large to store on GitHub without compression, so we'll unzip it into the temp directory, load it it into the global enviornment, and then save it as a compressed `R` data file (`.rda`):

```{r vacancy-data}
# unzip to temp
unzip(here("data", "raw", "nearby vacant parcels summary.zip"), 
      "nearby vacant parcels summary.csv", exdir = tmp)

# load data from temp
vacant <- readr::read_csv(file.path(tmp, "nearby vacant parcels summary.csv"))

# save as .rda
save(vacant, file = here("data", "vacant.rda"))
```

## Download Data
The reamining data sets are available via the City's Open Data website. Each will be downloaded, unzipped, and converted from the Microsoft Access format to `.rda` files.

### Parcel Data
First, we'll download and process the raw parcel data:

```{r parcel-data}
# download
download.file("https://www.stlouis-mo.gov/data/upload/data-files/prcl.zip", 
              file.path(tmp, "prcl.zip"))

# extract
unzip(file.path(tmp, "prcl.zip"), exdir = tmp)
prcl_db <- Hmisc::mdb.get(file.path(tmp, "prcl.mdb"))

# write
save(prcl_db, file = here("data", "raw", "prcl_db.rda"))
```

### Building Inspections
Next, we'll download and process the raw building inspection data:

### prmbdo.zip


### prmemp.zip



## Remove Temporary Directory
Finally, we'll ensure that the temporary directory is cleared from the disk before finishing:

```{r unlink}
unlink(tmp)
```


